\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-26 manuscript.Rnw
Pass hesim_data object to create_StateVals() rather than stateval_tbl()

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta",
  hesim_data = hesim_dat)
print(utility_tbl)
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma",
  hesim_data = hesim_dat)
print(medcost_tbl)
@

@@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed",
  hesim_data = hesim_dat
)
print(drugcost_tbl)
@

@@

<<ictstm_stvalmods>>=
# Utility
utilitymod <- create_StateVals(utility_tbl, n = n_samples)

# Costs
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
                                time_reset = TRUE)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples)
costmods <- list(Drug = drugcostmod,
                 Medical = medcostmod)
@

@@

<<psm_fits_soc>>=
fit_pfs_soc_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os, subset = (strategy_name == "SOC"),
  dist = "weibull")

fit_os_soc_wei <- flexsurvreg(
  Surv(os_time, os_status) ~  female,
  data = onc_pfs_os, subset = (strategy_name == "SOC"),
  dist = "weibull")

psmfit_soc_wei <- partsurvfit(
  flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
  data = onc_pfs_os
)
@

@@

<<psm_stateval_tbl>>=
attr(utility_tbl, "patients") <- hesim_dat$patients
attr(medcost_tbl, "patients") <- hesim_dat$patients
@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed",
  hesim_data = hesim_dat)
print(drugcost_tbl)
@

@@

<<psm_stvalmods>>=
utilitymod <- create_StateVals(utility_tbl, n = n_samples)
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples)
costmods <- list(Drug = drugcostmod, Medical = medcostmod)
@

>>>>

<<ictstm_utility>>=
utility_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(.8, .6),
             se = c(0.02, .05)
  ),
  dist = "beta")
print(utility_tbl)
@

@@

<<ictstm_medcosts>>=
medcost_tbl <- stateval_tbl(
  data.table(state_id = states$state_id,
             mean = c(2000, 9500),
             se = c(2000, 9500)
  ),
  dist = "gamma")
print(medcost_tbl)
@

@@

<<ictstm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt,
  dist = "fixed")
print(drugcost_tbl)
@

@@

<<ictstm_stvalmods>>=
# Utility
utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
                               hesim_data = hesim_dat)

# Costs
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
                                time_reset = TRUE, hesim_data = hesim_dat)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
                               hesim_data = hesim_dat)
costmods <- list(Drug = drugcostmod,
                 Medical = medcostmod)
@

@@

<<psm_fits_soc>>=
onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
fit_pfs_soc_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os_soc,
  dist = "weibull")

fit_os_soc_wei <- flexsurvreg(
  Surv(os_time, os_status) ~  female,
  data = onc_pfs_os_soc,
  dist = "weibull")

psmfit_soc_wei <- partsurvfit(
  flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
  data = onc_pfs_os_soc
)
@

@@

<<psm_drugcost>>=
drugcost_tbl <- stateval_tbl(
  drugcost_dt[time_start ==  0][, time_start := NULL],
  dist = "fixed")
print(drugcost_tbl)
@

@@

<<psm_stvalmods>>=
utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
                               hesim_data = hesim_dat)
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples, 
                                hesim_data = hesim_dat)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples, 
                               hesim_data = hesim_dat)
costmods <- list(Drug = drugcostmod, Medical = medcostmod)
@
